Verifying Demonstrations

### 2019-10-18 paper/DB-anon-cred.tex
Writes up proof for TF resistance

\daniel{Still intuition, we need the formal definition of security above.}
\begin{theorem}[\acs*{DBTF} resistance]
  \dots
\end{theorem}

\begin{proof}
  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
  provers help with non-negligible advantage~\(\epsilon < \frac{1}{2}\), \ie 
  the success probability is \(\frac{1}{2}+\epsilon\).
  The probability that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
  Since \(\epsilon\) is non-negligible, there is some case for which \(\adv\) 
  knows both responses.
  In that case \(\adv\) can simply compute the secret and impersonate with 
  probability \(1\) forever, which contradicts our assumption about 
  \(\epsilon\).
\end{proof}

>>>>

\daniel{Still intuition, we need the formal definition of security above.}
\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S}\) is negligible.
\end{theorem}

\begin{proof}
  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
  with non-negligible probability~\(\epsilon\) better than guessing, \ie a 
  success probability of \(\frac{1}{m^n}+\epsilon\).
  Say that \(\adv\) has successfully authenticated with the prover's help and 
  \(\S\) is given \(\adv\)'s state.

  Now \(\S\) will use \(\adv\) in a simulation.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge uniformly randomly.
  Since \(\adv\) cannot perform a relay to the prover and each challenge is 
  independent (uniformly random), the help provided by the prover must be 
  independent of the chosen challenge.
  Thus \(\S\) will provide the same help as before.

  When \(S\) has the second response it can compute the secret of the prover 
  and thus authenticate to the verifier with probability \(p_{\S} = 1\) in any 
  successive session.
  The same is true for \(\adv\) and thus \(p_{\adv} = p_{\S}\).
\end{proof}
